\section{Preliminaries}

We begin by formally stating the generalized form of the Erdős–Straus-type conjecture we propose:

\begin{conjecture}[Generalized Erdős–Straus Form]
For any integer $k \in \mathbb{N}$, the rational expression $\frac{2k}{n}$ can be represented as a sum of $(k+1)$ unit fractions. That is, for every pair $(k, n) \in \mathbb{N}^2$ with $n \geq 2$, there exists a set of natural numbers $\{ x_0, x_1, \dots, x_k \} \subset \mathbb{N}$ such that:
\[
\frac{2k}{n} = \frac{1}{x_0} + \frac{1}{x_1} + \cdots + \frac{1}{x_k} = \sum_{i=0}^{k} \frac{1}{x_i}.
\]
\end{conjecture}

We now justify the necessity of the condition $n \geq 2$ by establishing the following lemma:

\begin{lemma}
For every $k \in \mathbb{N}$, the equation in Conjecture~1 admits a solution when $n = 2$.
\end{lemma}

\begin{proof}
Substituting $n = 2$ into the conjectured identity, we aim to express:
\[
\frac{2k}{2} = k
\]
as a sum of $k+1$ unit fractions of natural numbers.

We construct the following multiset $S$ of size $k+1$:
\[
S = \underbrace{\{ 1, 1, \dots, 1 \}}_{k-1\text{ times}} \cup \{ 2, 2 \}.
\]

Clearly, the sum of the reciprocals of the elements in $S$ is:
\[
\left( \sum_{i=1}^{k-1} \frac{1}{1} \right) + \frac{1}{2} + \frac{1}{2} = (k-1) + \frac{1}{2} + \frac{1}{2} = k.
\]

Hence, the equality
\[
k = \sum_{i=0}^{k} \frac{1}{x_i}
\]
holds true for $x_i \in S$, satisfying the conjecture for $n = 2$. This completes the proof.
\end{proof}

One may naturally ask that, \emph{if by Lemma 1, the conjecture holds for $n=2$, then does it also holds for any $n \geq 2, \in \mathbb{N}$?}
This is specifically what builds the \emph{Conjecture 1}.

However, one can observe that when $n = 2p$ for some $p \in \mathbb{N}$, \emph{Conjecture 1} holds universally. To formalize this observation, we state the following lemma:

\begin{lemma}
Let $k \in \mathbb{N}$. If $n = 2p$ for some $p \in \mathbb{N}$, then \emph{Conjecture 1} holds.
\end{lemma}

\begin{proof}
Suppose $n = 2p$. Then the conjectured equation becomes:
\[
\frac{2k}{n} = \frac{k}{p} = \sum_{i=0}^{k} \frac{1}{x_i}, \quad x_i \in \mathbb{N}.
\]
This equality is satisfied by the multiset:
\[
X = \underbrace{\{ p, p, \dots, p \}}_{k-1 \text{ times}} \cup \{ 2p, 2p \},
\]
since:
\[
\sum_{i=1}^{k-1} \frac{1}{p} = \frac{k-1}{p}, \quad \text{and} \quad \frac{1}{2p} + \frac{1}{2p} = \frac{1}{p},
\]
yielding:
\[
\frac{k-1}{p} + \frac{1}{p} = \frac{k}{p}.
\]
Thus, the equality holds, and the lemma is proved.
\end{proof}

Consequently, the scope of \emph{Conjecture 1} reduces to the case where $n$ is an odd natural number greater than one. We therefore restate the conjecture more precisely as follows:

\begin{conjecture}
Let $k \in \mathbb{N}$, and let $n > 1$ be an odd natural number. Then the quantity $\frac{2k}{n}$ can be expressed as a sum of $k+1$ distinct unit fractions of positive integers.
\end{conjecture}

The remainder of this article is dedicated to establishing a proof of \emph{Conjecture 2}, which by \emph{Lemma 2}, implies the validity of \emph{Conjecture 1} in full generality.